\section{Implementation}
\label{sec:implementation}
% Put an introductory paragraph here that gives the reader an overview of what's coming. If there are multiple subsections, say in a few words or a sentence something about each subsection.

% include a separate subsection for each of the different implementations. Briefly describe your implementation, and include the use of compact pseudocode as necessary. The focus here should be on conciseness and clarity. Be sure to describe the strategy you used in parallelizing your code. Your example Listings should clearly indicate the OpenMP pragmas you used. 
In this study, we implemented two versions of a ray tracing system: a serial implementation (Serial RT) and a parallel implementation using OpenMP (OpenMP RT). These implementations were designed to explore the performance differences and challenges in parallelizing ray tracing on multi-core CPUs.

\input{03_1_ray-tracing-foundations}
\input{03_3_serial-rt}
\FloatBarrier
\input{03_4_openmp-rt}

\begin{comment}
%% the material that follows is from the generic tech paper skeleton project

\begin{itemize}
    \item Another way to look at this section is as a paper, within a paper, describing your implementation. That viewpoint makes this the introduction to the subordinate paper, which should describe the overall structure of your implementation and how it is designed to address the problem effectively.
\item Then, describe the structure of the rest of this section, and what each subsection describes.
\end{itemize}

How our solution (will | does) work
\begin{itemize}
    \item This is the body of the subordinate paper describing your solution. It may be divided into several subsections as required by the nature of your implementation.
    \item The level of detail about how the solution works is determined by what is appropriate to the type of paper (conference, journal, technical report).
    \item This section can be fairly short for conference papers, fairly long for journal papers, or quite long in technical reports. It all depends on the purpose of the paper and the target audience.
    \item Proposals are necessarily a good deal more vague in this section since you have to convince someone you know enough to have a good chance of building a solution, but that you have not already done so.
\end{itemize}

\end{comment}
